### 2020-09-29 README.Rmd
fixed link

0. [Objectives and Ideas](https://goodekat.github.io/LIME-research-journals/journals/00-objectives_and_ideas/00-objectives_and_ideas.html)
1. [Information on Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/01-hamby_data_and_models/01-hamby_data_and_models.html)
2. [Understanding LIME](https://goodekat.github.io/LIME-research-journals/journals/02-understanding_lime/02-understanding_lime.html)
3. [Applying LIME to Hamby Data](https://goodekat.github.io/LIME-research-journals/journals/03-applying_lime/03-applying_lime.html)
4. [Assessing LIME on Hamby Data](https://goodekat.github.io/LIME-research-journals/journals/04-assessing_lime/04-assessing_lime.html)
5. [Applying and Assessing LIME on Iris Data](https://goodekat.github.io/LIME-research-journals/journals/05-iris_comparison/05-iris_comparison.html)
6. [Notes on Readings](https://goodekat.github.io/LIME-research-journals/journals/06-literature_review/06-literature_review.html)
7. [Computational Issues](https://goodekat.github.io/LIME-research-journals/journals/07-computation_issues/07-computation_issues.html)
8. [LIME Applied to Logistic Regressions on Sine Data](https://goodekat.github.io/LIME-research-journals/journals/08-logistic_regression/08-logistic_regression.html)
9. [Identifying `rtrees` Training Data](https://goodekat.github.io/LIME-research-journals/journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.html)
10. [LIME Variability Across Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/10-lime_hamby_variability/10-LIME_hamby_variability.html)

>>>>

0. [Objectives and Ideas](https://goodekat.github.io/LIME-research-journals/journals/00-objectives_and_ideas/00-objectives_and_ideas.html)
1. [Information on Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/01-hamby_data_and_models/01-hamby_data_and_models.html)
2. [Understanding LIME](https://goodekat.github.io/LIME-research-journals/journals/02-understanding_lime/02-understanding_lime.html)
3. [Applying LIME to Hamby Data](https://goodekat.github.io/LIME-research-journals/journals/03-applying_lime/03-applying_lime.html)
4. [Assessing LIME on Hamby Data](https://goodekat.github.io/LIME-research-journals/journals/04-assessing_lime/04-assessing_lime.html)
5. [Applying and Assessing LIME on Iris Data](https://goodekat.github.io/LIME-research-journals/journals/05-iris_comparison/05-iris_comparison.html)
6. [Notes on Readings](https://goodekat.github.io/LIME-research-journals/journals/06-literature_review/06-literature_review.html)
7. [Computational Issues](https://goodekat.github.io/LIME-research-journals/journals/07-computation_issues/07-computation_issues.html)
8. [LIME Applied to Logistic Regressions on Sine Data](https://goodekat.github.io/LIME-research-journals/journals/08-logistic_regression/08-logistic_regression.html)
9. [Identifying rtrees Training Data](https://goodekat.github.io/LIME-research-journals/journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.html)
10. [LIME Variability Across Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/10-lime_hamby_variability/10-lime_hamby_variability.html)
